Discrete Probability for Discrete Quantum Computing

### 2016-04-30 prob.tex
a little cleanup; still not happy with interval prob

\begin{document}
\title{Probability}
\author{}
\date{\today}
\maketitle

@@

A \emph{probability
  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
specifies the necessary conditions for reasoning coherently about
collections of uncertain events. It consists of a \emph{sample space}
$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
  measure}~$\pmeas$. In this paper, we will only consider
\emph{finite} sets of events: we therefore define a sample space
$\Omega$ as an arbitrary non-empty finite set and the space of events
$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_i$,  of pairwise disjoint events, 
  $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space]
  Consider an experiment that tosses two coins. We have four possible
  outcomes that constitute the sample space
  $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
  for example the event $\{ HH, HT \}$ that the first coin is
  ``heads,'' the event $\{ HT, TH \}$ that the two coins land on
  opposite sides, and the event $\{ HT, TH, TT\}$ that at least one
  coin is tails. Here is a possible probability measure for these
  events:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
The assignment satisfies the two constraints for probability measures:
the probability of the entire sample space is 1, and the probability
of every collection of disjoint events (e.g.,
$\{ HT, TH \} = \{ HT \} \cup \{ TH \}$) is the sum of the individual
probabilities. The probability of collections of non-disjoint events
(e.g., $\{ HT, TH, TT \} = \{ HT, TH \} \cup \{ TH , TT \}$) may add
to something different than the probabilities of the individual
events. It is useful to think that this probability measure is
completely induced by the two coins in question and their
characteristics in the sense that each pair of coins induces a
measure, and each measure must correspond to some pair of coins.  In
this example, the first coin is twice as likely to be tails than heads
and the second coin is double-headed.  
\qed\end{example}

@@

\paragraph*{Set-valued Probability Measures.} The simplest such set,
and the one we will consider exclusively in this paper, is the set
$\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with the
operation $\vee$ where $x \vee y=\imposs$ if and only if
$x=y=\imposs$. In relation to the conventional definition, one can
interpret \imposs\ as the closed interval $[0,0]$, \poss\ as the
half-open interval $(0,1]$, and $\vee$ as the addition of
intervals. The definition of a probability measure in this case is
modified as being a function
$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = \poss$, and
\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup_i
E_i) = \bigvee_i \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space with finite set-valued
  probability measure] Under the new set-valued requirement, the
  probability measure in the first example becomes:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& \imposs \\
\pmeas(\{ HH \}) &=& \poss \\
\pmeas(\{ HT \}) &=& \imposs \\
\pmeas(\{ TH \}) &=& \poss \\
\pmeas(\{ TT \}) &=& \imposs \\
\pmeas(\{  HH, HT \}) &=& \poss \\
\pmeas(\{  HH, TH \}) &=& \poss \\
\pmeas(\{  HH , TT \}) &=& \poss \\
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& \poss \\
\pmeas(\{  HT , TT \}) &=& \imposs \\
\pmeas(\{  TH , TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH \}) &=& \poss \\
\pmeas(\{  HH, HT, TT \}) &=& \poss \\
\pmeas(\{  HH, TH, TT \}) &=& \poss \\
\pmeas(\{  HT, TH, TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH, TT \}) &=& \poss 
\end{array}
\end{array}\]
Despite the fact that we lost all numeric information, the probability
measure still reveals that the second coin is double-headed. We have
however lost the information regarding the bias in the first
coin. This information can be recovered with a more refined
probability measure as we show next. 
\qed\end{example}

\paragraph*{Interval-valued probability measures.} In this case, we
split the $[0,1]$ interval into a collection of overlapping closed
sub-intervals obeying certain restrictions to be described at the end
of the section. To illustrate the main ideas, we first consider a
simple example.

\begin{example}[Two-coin probability space with four intervals]
We split the interval in the following four closed sub-intervals:
\begin{itemize}
\item $[0,0]$ which we call \imposs, 
\item $[0,\frac{1}{2}]$ which we call \unlikely, 
\item $[\frac{1}{2},1]$ which we call \likely, and 
\item $[1,1]$ which we call \necess.
\end{itemize}
Using these new values, the probability measure becomes:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Not only does this probability measure reveal that the second coin is
double-headed but it also reveals that the first coin is more likely
to be tails than heads, despite the absence of numeric information.
\qed\end{example}

In interval-valued probability measures, if $\mu\left(E\right)=\left[a,b\right]$,
the left-endpoint~$a$ called belief denotes the strength of the
evidence that $E$ happens, and the right-endpoint~$b$ called plausibility
denotes the strength of the evidence that contradicts $E$. If we
define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we intuitively
have 
\begin{eqnarray*}
\pmeas\left(\emptyset\right) & = & \imposs\\
\pmeas\left(\Omega\right) & = & \necess\\
\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
\end{eqnarray*}
Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
then 
\begin{itemize}
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
\end{itemize}
Notice that the equality may not hold in general. This statement says
that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
putting all the evidences of $E_{i}$ together, but some evidence
may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
but may not equal. In our example, 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
 & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
\end{eqnarray*}
However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
because if we check the complement of $\{HH,TH\}$, we have 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
\end{eqnarray*}
and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
of $\{HH\}$ and $\{TH\}$ individually.

@@

\begin{example}[Two coin experiment] Consider an experiment that
  tosses two coins. We have four possible outcomes that constitute the
  sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
  first coin is ``heads'' is $\{ HH, HT \}$; the event that the two
  coins land on opposite sides is $\{ HT, TH \}$; the event that at
  least one coin is tails is $\{ HT, TH, TT\}$. Depending on the
  assumptions regarding the coins, we can define several probability
  measures. Here is a possible one:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
\end{example}

>>>>

\begin{document}
\title{Discrete Probability for Discrete Quantum Computing}
\author{}
\date{\today}
\maketitle

@@

A \emph{probability
  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
specifies the necessary conditions for reasoning coherently about
collections of uncertain events. It consists of a \emph{sample space}
$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
  measure}~$\pmeas$. In this paper, we will only consider
\emph{finite} sets of events: we therefore define a sample space
$\Omega$ as an arbitrary non-empty finite set and the space of events
$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_i$ of pairwise disjoint events, 
  $\pmeas(\bigcup_i E_i) = \sum_i \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space]\label{ex1}
  Consider an experiment that tosses two coins. We have four possible
  outcomes that constitute the sample space
  $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
  for example the event $\{ HH, HT \}$ that the first coin lands heads
  up, the event $\{ HT, TH \}$ that the two coins land on opposite
  sides, and the event $\{ HT, TH, TT\}$ that at least one coin lands
  tails up. Here is a possible probability measure for these events:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
The assignment satisfies the two constraints for probability measures:
the probability of the entire sample space is 1, and the probability
of every collection of disjoint events (e.g.,
$\{ HT, TH \} = \{ HT \} \cup \{ TH \}$) is the sum of the individual
probabilities. The probability of collections of non-disjoint events
(e.g., $\{ HT, TH, TT \} = \{ HT, TH \} \cup \{ TH , TT \}$) may add
to something different than the probabilities of the individual
events. It is useful to think that this probability measure is
completely induced by the two coins in question and their
characteristics in the sense that each pair of coins induces a
measure, and each measure must correspond to some pair of coins.  The
measure above is induced by two coins such that the first coin is
twice as likely to land tails up than heads up and the second coin is
double-headed.  
\qed\end{example}

@@

\paragraph*{Set-valued Probability Measures.} The simplest such set is
the set $\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with
the operation $\vee$ where $x \vee y=\imposs$ if and only if
$x=y=\imposs$. In relation to the conventional definition, one can
interpret \imposs\ as the closed interval $[0,0]$, \poss\ as the
half-open interval $(0,1]$, and $\vee$ as the addition of
intervals. The definition of a probability measure in this case is
modified to a function $\pmeas : \events \rightarrow \mathscr{L}_{2}$
such that:
\begin{itemize}
\item $\pmeas(\Omega) = \poss$, and
\item for a collection $E_i$ of pairwise disjoint events, $\pmeas(\bigcup_i
E_i) = \bigvee_i \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space with finite set-valued
  probability measure] \label{ex2} Under the new set-valued
  requirement, the probability measure in the first example becomes:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& \imposs \\
\pmeas(\{ HH \}) &=& \poss \\
\pmeas(\{ HT \}) &=& \imposs \\
\pmeas(\{ TH \}) &=& \poss \\
\pmeas(\{ TT \}) &=& \imposs \\
\pmeas(\{  HH, HT \}) &=& \poss \\
\pmeas(\{  HH, TH \}) &=& \poss \\
\pmeas(\{  HH , TT \}) &=& \poss \\
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& \poss \\
\pmeas(\{  HT , TT \}) &=& \imposs \\
\pmeas(\{  TH , TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH \}) &=& \poss \\
\pmeas(\{  HH, HT, TT \}) &=& \poss \\
\pmeas(\{  HH, TH, TT \}) &=& \poss \\
\pmeas(\{  HT, TH, TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH, TT \}) &=& \poss 
\end{array}
\end{array}\]
Despite the fact that we have lost all numeric information, the
probability measure still reveals that the second coin is
double-headed. We have however lost the information regarding the bias
in the first coin. This information can be recovered with a more
refined probability measure as we show next.  
\qed\end{example}

\paragraph*{Interval-valued probability measures.} In this case, we
split the $[0,1]$ interval into a collection of overlapping closed
sub-intervals obeying certain restrictions to be described at the end
of the section. First we illustrate the main ideas using a simple
example.

\begin{example}[Two-coin probability space with four intervals] \label{ex3}
We split the unit interval $[0,1]$ in the following four closed sub-intervals:
\begin{itemize}
\item $[0,0]$ which we call \imposs, 
\item $[0,\frac{1}{2}]$ which we call \unlikely, 
\item $[\frac{1}{2},1]$ which we call \likely, and 
\item $[1,1]$ which we call \necess.
\end{itemize}
Using these new values, the probability measure becomes:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Not only does this probability measure reveal that the second coin is
double-headed but it also reveals the bias in the first coin, again despite
the absence of any numeric information.  
\qed\end{example}

The probability measure above can be understood in reference to
Ex.~\ref{ex1} by mapping each numeric value to the smallest interval
containing it. The probability measure appears quite intuitive from
that perspective. However, if we attempt to understand the probability
measure independently of Ex.~\ref{ex1} we would hard pressed to
justify the following assignments:
\[ 
\pmeas(\{HH\}) = \unlikely, \quad\pmeas(\{TH\}) = \likely, \quad
\pmeas(\{HH\}\cup\{TH\}) = \necess 
\]
which assert that an \unlikely-event whose probability is in the range
$[0,\frac{1}{2}]$ and a \likely-event whose probability is in the
range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
is in the range $[1,1]$! To understand this mystery, it is important
to investigate the mathematical definition of interval-valued
probabilities in detail.

In interval-valued probability measures, if the probability of an
event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
representing the strength of the evidence that supports $E$, and the
right-endpoint~$b$ as the strength of the evidence that contradicts
$E$. If we define $1-\left[a,b\right]=\left[1-b,1-a\right]$, then we
intuitively have
\begin{eqnarray*}
\pmeas\left(\emptyset\right) & = & \imposs\\
\pmeas\left(\Omega\right) & = & \necess\\
\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
\end{eqnarray*}
Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
then 
\begin{itemize}
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
\end{itemize}
Notice that the equality may not hold in general. This statement says
that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
putting all the evidences of $E_{i}$ together, but some evidence
may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
but may not equal. In our example, 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
 & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
\end{eqnarray*}
However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
because if we check the complement of $\{HH,TH\}$, we have 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
\end{eqnarray*}
and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
of $\{HH\}$ and $\{TH\}$ individually.

@@

\begin{example}[Two coin experiment] Consider an experiment that
  tosses two coins. We have four possible outcomes that constitute the
  sample space $\Omega = \{ HH, HT, TH, TT \}$. The event that the
  first coin lands heads up is $\{ HH, HT \}$; the event that the two
  coins land on opposite sides is $\{ HT, TH \}$; the event that at
  least one coin lands tails up is $\{ HT, TH, TT\}$. Depending on the
  assumptions regarding the coins, we can define several probability
  measures. Here is a possible one:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
\end{example}
